\documentclass[runningheads,8pt]{llncs}
\setcounter{secnumdepth}{4}
%
\usepackage[numbers]{natbib}
\usepackage{multirow}
\usepackage{url,bm}
\usepackage[breaklinks=true,unicode=true,urlcolor = blue,colorlinks = true,citecolor = blue,linkcolor = blue]{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
%
%\usepackage{geometry}
%\geometry{a4paper,portrait}  % Set paper/media size and orientation.
%\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
%
\graphicspath{{./figs/}}
%
\renewcommand\bibname{References}
%
\renewcommand{\vec}[1]{\bm{#1}}
% Define Authors
%
% 
\urldef{\mailsa}\path|{k.yershov@ifw-dresden.de,|
	\urldef{\mailsb}\path|o.volkov@hzdr.de}|   
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
	\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}
%\preprint{\textcolor[rgb]{0.00,0.50,0.75}{\texttt{Draft \gitAbbrevHash{} by \gitCommitterName{} on \gitCommitterIsoDate}}}	
	\mainmatter  % start of an individual contribution
	
	% first the title is needed
	\title{Flat curved systems}
	
	% a short form should be given in case it is too long for the running head
	\titlerunning{Flat curved systems}
	
	% the name(s) of the author(s) follow(s) next
	%
	% NB: Chinese authors should write their first names(s) in front of
	% their surnames. This ensures that the names appear correctly in
	% the running heads and the author index.
	%
	\author{Kostiantyn V. Yershov$^{1,2}$ \and Oleksii M. Volkov$^{3}$}
	%
	\authorrunning{Flat curved systems: Kostiantyn V. Yershov and Oleksii M. Volkov}
	% (feature abused for this document to repeat the title also on left hand pages)
	
	% the affiliations are given next; don't give your e-mail address
	% unless you accept that it will be published
	\institute{$^1$Bogolyubov Institute for Theoretical Physics of NAS of Ukraine,\\
		Metrologichna str. 14,  03143 Kyiv, Ukraine\\
		$^2$Leibniz-Institut f\"ur Festk\"orper- und Werkstoffforschung, IFW Dresden,\\
		 Helmholtzstra{\ss}e 20, D-01171 Dresden, Germany\\
		 $^{3}$Helmholtz-Zentrum Dresden-Rossendorf e. V. Institute of Ion Beam Physics and Materials Research,
		 Bautzner Landstra{\ss}e 400, 01328 Dresden, Germany\\
		\mailsa
		\mailsb}
	
	%
	% NB: a more complex sample for affiliations and the mapping to the
	% corresponding authors can be found in the file "llncs.dem"
	% (search for the string "\mainmatter" where a contribution starts).
	% "llncs.dem" accompanies the document class "llncs.cls".
	%
	
	\toctitle{Flat curved systems}
	\tocauthor{Kostiantyn V. Yershov and Oleksii M. Volkov}
	\maketitle
	
	
\begin{abstract}
	In this chapter we consider the flat curved ferromagnetic quasi one-dimensionless systems. We present (i) the general toolbox for description of magnetic properties of the curvilinear ferromagnetic wires and ribbons, (ii) the available methods for fabrication and characterization of curved systems.  The presented methods are illustrated on the different geometries. 
	\keywords{Ferromagnets, curvilinear geometry, exchange interaction.}
\end{abstract}
	
%\tableofcontents
%\clearpage	
%\input{1_introduction}

Recent advances in the fabrication of curvilinear magnets \cite{Streubel16a,Fernandez17,Ball17,Sanz-Hernandez18,Huth18,Huth20,Sanz-Hernandez20} raises the question of the influence of curvature on statics and dynamics of a magnetization. For spintronic devices the geometrically induced potentials arising from curved shapes gain practical importance. For example, designs of these devices require wires with curvilinear segments, e.g. vertical U-shaped configuration increases the storage density of the potential magnetic racetrack memory devices~\cite{Parkin08,Zhang15}.
...

{\color{red} I don't know, do we need the introduction in here?} 

\input{2_theory}

\input{3_fabrication}

\input{4_characterization}

\bibliographystyle{splncs}
\bibliography{soliton}
\end{document}
